---
title: "Difference-in-Differences"
subtitle: "The 2×2, staggered adoption, synthetic DiD, and common pitfalls"
author: "Daniel Winkler"
date: today
format:
  revealjs:
    slide-number: true
    embed-resources: true
    html-math-method: katex
    fig-width: 9
    fig-height: 4.8
    fig-align: center
    code-overflow: wrap
    code-line-numbers: false
execute:
  echo: false
  warning: false
  message: false
params:
  # Set to false for a learner version: planted effects from
  # instructor_truth/ are then neither read nor shown.
  show_truth: true
---

```{r}
#| label: setup
#| include: false
# Render from did_teaching_data/: quarto render did_lecture_slides.qmd
suppressPackageStartupMessages({
  library(dplyr)
  library(fixest)
  library(ggplot2)
  library(did)
  library(panelView)
  library(WeightIt)
  library(synthdid)
  library(cobalt)
  library(bacondecomp)
})
options(scipen = 6, knitr.kable.NA = "")
theme_set(theme_minimal(base_size = 15))
# Whole-week ticks for every plot with weeks on the x axis.
week_axis <- scale_x_continuous(breaks = scales::breaks_width(2))

data_dir <- "data"
truth_dir <- "instructor_truth"
show_truth <- isTRUE(params$show_truth)

read_case <- function(case_id) {
  read.csv(
    file.path(data_dir, sprintf("case_%s.csv", case_id)),
    stringsAsFactors = FALSE
  )
}

read_truth <- function(case_id) {
  read.csv(file.path(truth_dir, sprintf("case_%s_truth.csv", case_id)))
}

# Planted ATT over the treated cells; NA when rendered without truth.
true_att <- function(case_id) {
  if (!show_truth) {
    return(NA_real_)
  }
  truth <- read_truth(case_id)
  mean(truth$tau[truth$treated == 1])
}

fmt <- function(x, digits = 3) formatC(x, format = "f", digits = digits)

# Estimate and standard error of one fixest coefficient.
coef_se <- function(fit, term = "treated") {
  unname(coeftable(fit)[term, c("Estimate", "Std. Error")])
}

estimate_table <- function(specification, estimate, standard_error, case_id) {
  out <- data.frame(
    Specification = specification,
    Estimate = estimate,
    `Std. error` = standard_error,
    check.names = FALSE
  )
  if (show_truth) {
    out$`Planted ATT` <- true_att(case_id)
  }
  knitr::kable(out, digits = 3)
}

first_adoption <- function(d) {
  min(d$adoption_period[d$ever_treated == 1], na.rm = TRUE)
}

plot_means <- function(d, group_var, vlines, title, subtitle = NULL) {
  means <- d |>
    summarise(.by = c(period, {{ group_var }}), mean_outcome = mean(outcome))
  ggplot(
    means,
    aes(
      x = period,
      y = mean_outcome,
      color = {{ group_var }},
      shape = {{ group_var }}
    )
  ) +
    geom_vline(xintercept = vlines, linetype = "dashed", color = "grey40") +
    geom_line() +
    geom_point(size = 2) +
    labs(
      title = title,
      subtitle = subtitle,
      x = "Week",
      y = "Mean log revenue",
      color = NULL,
      shape = NULL
    ) +
    week_axis +
    theme(legend.position = "bottom")
}

# Calendar-period event study with the treated-group interaction.
fit_event <- function(d, ref) {
  feols(
    as.formula(sprintf(
      "outcome ~ i(period, ever_treated, ref = %d) | unit_id + period",
      ref
    )),
    vcov = ~unit_id,
    data = d
  )
}

# Joint Wald p-value that all pre-period coefficients before `ref` are zero.
pre_test_p <- function(fit, ref) {
  leads <- paste(seq_len(ref - 1L), collapse = "|")
  wald(fit, keep = sprintf("^period::(%s):", leads), print = FALSE)$p
}

# Event-study coefficients as a data frame, with the reference period at 0.
event_df <- function(fit, ref) {
  ct <- coeftable(fit)
  out <- data.frame(
    event_time = as.integer(sub(
      "^[A-Za-z_]+::(-?[0-9]+).*$",
      "\\1",
      rownames(ct)
    )),
    estimate = unname(ct[, "Estimate"]),
    se = unname(ct[, "Std. Error"])
  )
  bind_rows(out, data.frame(event_time = ref, estimate = 0, se = 0)) |>
    arrange(event_time)
}

plot_event <- function(es, xlab, ref, truth = NULL) {
  p <- ggplot(es, aes(x = event_time, y = estimate)) +
    geom_hline(yintercept = 0, color = "grey50") +
    geom_vline(xintercept = ref + 0.5, linetype = "dashed", color = "grey40")
  if (!is.null(truth)) {
    p <- p +
      geom_line(
        data = truth,
        aes(x = event_time, y = estimate),
        color = "firebrick",
        linetype = "dotted",
        linewidth = 1
      )
  }
  p +
    geom_pointrange(aes(ymin = estimate - 1.96 * se, ymax = estimate + 1.96 * se)) +
    labs(x = xlab, y = "Estimate and 95% CI") +
    week_axis
}

cs_data <- function(d) {
  d |>
    mutate(
      id_num = as.integer(sub("^unit_", "", unit_id)),
      cohort = if_else(is.na(adoption_period), 0, adoption_period)
    )
}

fit_cs <- function(d, xformla = ~1, est_method = "dr",
                   control_group = "nevertreated", ...) {
  att_gt(
    yname = "outcome",
    tname = "period",
    idname = "id_num",
    gname = "cohort",
    xformla = xformla,
    data = cs_data(d),
    est_method = est_method,
    control_group = control_group,
    bstrap = FALSE,
    panel = TRUE,
    print_details = FALSE,
    ...
  )
}

cs_agg <- function(cs_fit, type = "simple") {
  aggte(cs_fit, type = type, bstrap = FALSE, cband = FALSE)
}

cs_event_df <- function(cs_dynamic) {
  data.frame(
    event_time = as.integer(cs_dynamic$egt),
    estimate = unname(cs_dynamic$att.egt),
    se = unname(cs_dynamic$se.egt)
  )
}

fit_sdid <- function(d) {
  panel <- panel.matrices(
    d,
    unit = "unit_id",
    time = "period",
    outcome = "outcome",
    treatment = "treated"
  )
  fit <- synthdid_estimate(panel$Y, panel$N0, panel$T0)
  list(
    fit = fit,
    panel = panel,
    estimate = as.numeric(fit),
    se = sqrt(vcov(fit, method = "jackknife"))[1, 1]
  )
}
```

## Roadmap {.smaller}

| Case | What it teaches |
|---|---|
| 01 | The 2×2, TWFE, event study, placebo, Callaway–Sant'Anna, synthetic DiD |
| 02 | Parallel trends within covariate groups; weighting |
| 03 | Selection on a temporary dip before adoption |
| 04–05 | Staggered adoption and the Goodman-Bacon decomposition |
| 06 | Spillovers to control stores |
| 07 | Effects that differ by an observed store characteristic |
| 08 | Controlling for a mediator (optional) |

# Case 01: the 2×2 benchmark

## Case 01: loyalty offer in half the stores

```{r}
#| label: case01-data
#| fig-height: 4.4
d01 <- read_case("01")
g01 <- first_adoption(d01)
panelview(
  outcome ~ treated,
  data = d01,
  index = c("unit_id", "period"),
  pre.post = TRUE,
  by.timing = TRUE,
  axis.adjust = TRUE,
  axis.lab = "time",
  main = "Case 01: treatment status by store and week"
)
```

## Look at the group means first

```{r}
#| label: case01-means
#| fig-height: 4.4
d01 |>
  mutate(group = if_else(ever_treated == 1, "Treated", "Control")) |>
  plot_means(group, g01, "Case 01: mean outcome by group", "Dashed line: launch in week 7")
```

## What DiD estimates

Potential outcomes $Y_{it}(1)$ and $Y_{it}(0)$; treatment starts in week $g$.

$$
\text{ATT} = \mathbb{E}\big[\,Y_{it}(1) - Y_{it}(0) \mid \text{treated},\ t \ge g\,\big]
$$

For treated stores after launch, $Y_{it}(0)$ is never observed. DiD fills it in with the control group's change over the same weeks.

In every case the outcome is log weekly revenue and standard errors are clustered by unit.`r if (show_truth) " Tables show the planted ATT, the true effect in the simulation." else ""`

## What DiD assumes

1. **Parallel trends**: without treatment, treated and control units would have changed by the same amount on average.
2. **No anticipation**: before week $g$, treated units' outcomes equal $Y(0)$.
3. **SUTVA** (stable unit treatment value assumption), here no interference: a control unit's outcome does not depend on who is treated.

Parallel trends concerns changes over time; fixed effects absorb time-invariant (constant) differences.

## The 2×2 by hand

```{r}
#| label: case01-2x2
cell_means_01 <- d01 |>
  mutate(
    group = if_else(ever_treated == 1, "Treated", "Control"),
    window = if_else(period >= g01, "Post", "Pre")
  ) |>
  summarise(.by = c(group, window), mean_outcome = mean(outcome))
m01 <- function(grp, win) {
  cell_means_01$mean_outcome[cell_means_01$group == grp & cell_means_01$window == win]
}
two_by_two_01 <- data.frame(
  Group = c("Treated", "Control"),
  Pre = c(m01("Treated", "Pre"), m01("Control", "Pre")),
  Post = c(m01("Treated", "Post"), m01("Control", "Post"))
) |>
  mutate(Change = Post - Pre)
did_by_hand_01 <- diff(rev(two_by_two_01$Change))
knitr::kable(two_by_two_01, digits = 3)
```

$$
\begin{aligned}
\widehat{\text{DiD}} &= (\bar y_{T,\text{post}} - \bar y_{T,\text{pre}}) - (\bar y_{C,\text{post}} - \bar y_{C,\text{pre}}) \\
&= (`r fmt(m01("Treated", "Post"))` - `r fmt(m01("Treated", "Pre"))`) - (`r fmt(m01("Control", "Post"))` - `r fmt(m01("Control", "Pre"))`) \\
&= `r fmt(m01("Treated", "Post") - m01("Treated", "Pre"))` - `r fmt(m01("Control", "Post") - m01("Control", "Pre"))` \\
&= `r fmt(did_by_hand_01)`
\end{aligned}
$$

## The same number from a regression

$$
y_{it} = \alpha_i + \lambda_t + \beta\, D_{it} + \varepsilon_{it}
$$

$D_{it} = \text{Treated}_i \times \text{Post}_t$ is `treated`: 1 only for treated-group stores in weeks `r g01`–`r max(d01$period)`. It is not `ever_treated`, which $\alpha_i$ absorbs.

```{r}
#| label: case01-twfe
#| echo: true
twfe_fit_01 <- feols(outcome ~ treated | unit_id + period,
                     vcov = ~unit_id, data = d01)
```

```{r}
#| label: case01-twfe-compare
twfe_01 <- coef_se(twfe_fit_01)
```

Two-way fixed effects (TWFE): $\hat\beta =$ `r fmt(twfe_01[1], 4)` (SE `r fmt(twfe_01[2], 4)`). The 2×2 by hand: `r fmt(did_by_hand_01, 4)`.

With one adoption date and a balanced panel, TWFE *is* the 2×2.

## Event study: inspect the pre-period

$$
y_{it} = \alpha_i + \lambda_t + \textstyle\sum_{k \ne `r g01 - 1`} \beta_k\, \mathbf{1}\{t = k\}\cdot \text{Treated}_i + \varepsilon_{it}
$$

```{r}
#| label: case01-event
#| fig-height: 3.4
event_fit_01 <- fit_event(d01, g01 - 1L)
pre_p_01 <- pre_test_p(event_fit_01, g01 - 1L)
plot_event(event_df(event_fit_01, g01 - 1L), "Week (week 6 is the reference)", g01 - 1L)
```

Joint Wald test that weeks 1–5 are zero: p = `r fmt(pre_p_01)`.

## Placebo: pretend treatment started earlier

```{r}
#| label: case01-placebo
#| echo: true
placebo_fit_01 <- feols(
  outcome ~ placebo_treated | unit_id + period,
  vcov = ~unit_id,
  data = d01 |>
    filter(period < g01) |>
    mutate(
      placebo_treated = as.integer(ever_treated == 1 & period >= g01 - 3L)
    )
)
```

```{r}
#| label: case01-placebo-result
placebo_01 <- coef_se(placebo_fit_01, "placebo_treated")
```

A fake week-4 launch, using pre-launch weeks only: `r fmt(placebo_01[1])` (SE `r fmt(placebo_01[2])`).

The placebo and the event-study leads use the same pre-period comparison. Neither tests parallel trends after launch.

## Two alternatives to TWFE

**Callaway–Sant'Anna**: estimate $\text{ATT}(g,t)$ for each cohort $g$ and week $t$ from one clean 2×2 against never-treated units, measured from week $g-1$. Then average the $\text{ATT}(g,t)$ with weights you choose.

**Synthetic DiD** (Arkhangelsky et al. 2021): reweight control units so their pre-launch path parallels the treated path, and reweight pre-launch weeks to resemble the post-launch weeks. Then run DiD on the weighted panel.

$$
\hat\tau = \arg\min_{\tau,\mu,\alpha,\beta} \textstyle\sum_{i,t} \big(y_{it} - \mu - \alpha_i - \beta_t - D_{it}\,\tau\big)^2\ \hat\omega_i\,\hat\lambda_t
$$

## Case 01: the estimators agree

```{r}
#| label: case01-compare
cs_fit_01 <- fit_cs(d01)
cs_01 <- cs_agg(cs_fit_01)
sdid_01 <- fit_sdid(d01)
estimate_table(
  c("TWFE", "Callaway–Sant'Anna", "Synthetic DiD"),
  c(twfe_01[1], cs_01$overall.att, sdid_01$estimate),
  c(twfe_01[2], cs_01$overall.se, sdid_01$se),
  "01"
)
```

In a clean design the alternatives add little. Each later case changes one thing about this design.

## Case 01: synthetic DiD's fit

```{r}
#| label: sdid-01
#| fig-height: 4.4
plot(sdid_01$fit, overlay = 1) +
  labs(x = "Week", y = "Mean log revenue") +
  week_axis
```

# Case 02: parallel trends within groups

## Case 02: CRM adoption varies with growth segment

```{r}
#| label: case02-means
#| fig-height: 4.2
d02 <- read_case("02")
g02 <- first_adoption(d02)
# Color by segment, line type by treatment: each segment's treated and control
# paths sit side by side.
d02 |>
  mutate(group = if_else(ever_treated == 1, "Treated", "Control")) |>
  summarise(.by = c(period, growth_segment, group), mean_outcome = mean(outcome)) |>
  ggplot(aes(
    x = period,
    y = mean_outcome,
    color = growth_segment,
    linetype = group,
    shape = group,
    group = interaction(growth_segment, group)
  )) +
  geom_vline(xintercept = g02, linetype = "dashed", color = "grey40") +
  geom_line() +
  geom_point(size = 2) +
  labs(
    title = "Case 02: means by treatment and growth segment",
    x = "Week",
    y = "Mean log revenue",
    color = "Growth segment",
    linetype = NULL,
    shape = NULL
  ) +
  week_axis +
  theme(legend.position = "bottom")
```

High-growth retailers adopt more often and grow faster anyway.

## Case 02: adjust for the segment {.smaller}

```{r}
#| label: case02-estimates
twfe_02 <- coef_se(feols(outcome ~ treated | unit_id + period, vcov = ~unit_id, data = d02))
baseline_02 <- d02 |>
  filter(period == min(period)) |>
  distinct(unit_id, ever_treated, growth_segment)
ipw_02 <- weightit(ever_treated ~ growth_segment, data = baseline_02, method = "glm", estimand = "ATT")
d02_ipw <- d02 |>
  left_join(baseline_02 |> mutate(ipw_weight = ipw_02$weights) |> select(unit_id, ipw_weight), by = "unit_id")
ipw_twfe_02 <- coef_se(feols(outcome ~ treated | unit_id + period, weights = ~ipw_weight, vcov = ~unit_id, data = d02_ipw))
cs_02 <- cs_agg(fit_cs(d02, xformla = ~growth_segment, est_method = "ipw"))
sdid_02 <- fit_sdid(d02)
estimate_table(
  c(
    "TWFE, no adjustment",
    "TWFE weighted by inverse propensity (segment)",
    "Callaway–Sant'Anna IPW (segment)",
    "Synthetic DiD (no covariates)"
  ),
  c(twfe_02[1], ipw_twfe_02[1], cs_02$overall.att, sdid_02$estimate),
  c(twfe_02[2], ipw_twfe_02[2], cs_02$overall.se, sdid_02$se),
  "02"
)
```

Inverse-propensity weighting (IPW) reweights controls to the treated segment mix. It assumes trends are parallel within segments and that every segment has both treated and control retailers.

## Case 02: check what the weights do

```{r}
#| label: case02-balance
#| fig-height: 3.6
balance_02 <- bal.tab(ipw_02, un = TRUE, disp = "means")
love.plot(ipw_02, thresholds = c(m = 0.1), title = NULL)
```

The effective sample size of the weighted controls is `r fmt(balance_02$Observations["Adjusted", "Control"], 1)` of `r balance_02$Observations["Unadjusted", "Control"]`: extreme weights mean a few controls carry the estimate.

## Case 02: synthetic DiD's fit

```{r}
#| label: sdid-02
#| fig-height: 4.4
plot(sdid_02$fit, overlay = 1) +
  labs(x = "Week", y = "Mean log revenue") +
  week_axis
```

## Case 02: where synthetic DiD puts its weight

```{r}
#| label: sdid-02-weights
omega_02 <- attr(sdid_02$fit, "weights")$omega
controls_02 <- data.frame(
  unit_id = rownames(sdid_02$panel$Y)[seq_len(sdid_02$panel$N0)],
  omega = omega_02
) |>
  left_join(baseline_02, by = "unit_id")
treated_mix_02 <- baseline_02 |>
  filter(ever_treated == 1) |>
  count(growth_segment) |>
  mutate(share = n / sum(n))
controls_02 |>
  summarise(.by = growth_segment, `Unweighted control share` = n() / nrow(controls_02), `Synthetic DiD weight` = sum(omega)) |>
  left_join(treated_mix_02 |> select(growth_segment, `Treated share` = share), by = "growth_segment") |>
  arrange(growth_segment) |>
  rename(Segment = growth_segment) |>
  knitr::kable(digits = 3)
```

Synthetic DiD never sees the segment. Matching pre-launch paths moves weight toward high-growth controls. Estimate `r fmt(sdid_02$estimate)` against unadjusted TWFE `r fmt(twfe_02[1])`.

# Case 03: selection before adoption

## Case 03: stores adopt after a sales slump

```{r}
#| label: case03-means
#| fig-height: 4.4
d03 <- read_case("03")
g03 <- first_adoption(d03)
d03 |>
  mutate(group = if_else(ever_treated == 1, "Treated", "Control")) |>
  plot_means(group, g03, "Case 03: mean outcome by group")
```

## Case 03: the dip shows in the event study

```{r}
#| label: case03-event
#| fig-height: 4.2
event_fit_03 <- fit_event(d03, g03 - 1L)
pre_p_03 <- pre_test_p(event_fit_03, g03 - 1L)
plot_event(event_df(event_fit_03, g03 - 1L), "Week (week 6 is the reference)", g03 - 1L)
```

Pre-test p = `r fmt(pre_p_03)`: adopting stores dip in weeks 5–6, then recover.

## Case 03: which baseline? {.smaller}

```{r}
#| label: case03-estimates
twfe_03 <- coef_se(feols(outcome ~ treated | unit_id + period, vcov = ~unit_id, data = d03))
cs_03 <- cs_agg(fit_cs(d03))
cs_dip_03 <- cs_agg(fit_cs(d03, anticipation = 2))
sdid_03 <- fit_sdid(d03)
estimate_table(
  c("TWFE", "Synthetic DiD", "Callaway–Sant'Anna, base week 6", "Callaway–Sant'Anna, anticipation = 2 (base week 4)"),
  c(twfe_03[1], sdid_03$estimate, cs_03$overall.att, cs_dip_03$overall.att),
  c(twfe_03[2], sdid_03$se, cs_03$overall.se, cs_dip_03$overall.se),
  "03"
)
```

- TWFE and synthetic DiD average the dip into the baseline; the default Callaway–Sant'Anna baseline, week 6, is the bottom of the dip.
- `anticipation = 2` moves the baseline to week 4. This assumes the slump would have reversed without the software, which the data cannot show.

# Cases 04–05: staggered adoption

## Cases 04 and 05: three cohorts plus never-treated

```{r}
#| label: stagger-data
#| fig-height: 4.2
d04 <- read_case("04")
d05 <- read_case("05")
panelview(
  outcome ~ treated,
  data = d05,
  index = c("unit_id", "period"),
  pre.post = TRUE,
  by.timing = TRUE,
  axis.adjust = TRUE,
  axis.lab = "time",
  main = "Case 05: treatment status by market and week"
)
```

Both cases share the same adoption timing. The effect is constant in Case 04 and grows with exposure in Case 05.

## Cohort means

```{r}
#| label: stagger-means
#| fig-height: 4.4
bind_rows(
  d04 |> mutate(case = "Case 04: constant effect"),
  d05 |> mutate(case = "Case 05: growing effect")
) |>
  mutate(cohort = if_else(is.na(adoption_period), "Never treated", paste("Adopts week", adoption_period))) |>
  summarise(.by = c(case, period, cohort), mean_outcome = mean(outcome)) |>
  ggplot(aes(x = period, y = mean_outcome, color = cohort)) +
  geom_vline(xintercept = sort(unique(na.omit(d05$adoption_period))), linetype = "dashed", color = "grey60") +
  geom_line() +
  geom_point(size = 1.5) +
  facet_wrap(~case) +
  labs(x = "Week", y = "Mean log revenue", color = NULL) +
  week_axis +
  theme(legend.position = "bottom")
```

## TWFE breaks only when effects change over time {.smaller}

```{r}
#| label: stagger-table
sunab_data <- function(d) d |> mutate(cohort = if_else(is.na(adoption_period), 10000, adoption_period))
stagger_rows <- lapply(c("04", "05"), function(id) {
  d <- read_case(id)
  tw <- coef_se(feols(outcome ~ treated | unit_id + period, vcov = ~unit_id, data = d))
  cs <- cs_agg(fit_cs(d))
  sa <- summary(feols(outcome ~ sunab(cohort, period) | unit_id + period, vcov = ~unit_id, data = sunab_data(d)), agg = "ATT")
  sa <- unname(coeftable(sa)["ATT", c("Estimate", "Std. Error")])
  out <- data.frame(
    Case = id,
    Estimator = c("TWFE", "Callaway–Sant'Anna", "Sun–Abraham"),
    Estimate = c(tw[1], cs$overall.att, sa[1]),
    `Std. error` = c(tw[2], cs$overall.se, sa[2]),
    check.names = FALSE
  )
  if (show_truth) out$`Planted ATT` <- true_att(id)
  out
})
stagger_table <- do.call(rbind, stagger_rows)
knitr::kable(stagger_table, digits = 3)
```

Parallel trends holds in both cases. The TWFE gap in Case 05 comes from the estimator.

## Goodman-Bacon (2021): TWFE averages 2×2s {.smaller}

| Comparison | Treated | Control | Window | Clean? |
|---|---|---|---|---|
| Treated vs never treated | cohort $k$ | never treated | all weeks | yes |
| Earlier vs later | early cohort $k$ | late cohort $l$, not yet treated | before $l$ adopts | yes |
| Later vs earlier | late cohort $l$ | early cohort $k$, **already treated** | after $k$ adopts | **no** |

- The weights depend only on cohort sizes and timing. Cohorts treated for about half the panel get the most weight.
- In "later vs earlier", an already-treated cohort is the control. If its effect is still changing, that change is subtracted.

## A toy panel with a growing effect

```{r}
#| label: toy
#| fig-height: 4
toy <- expand.grid(unit = 1:20, period = 1:10) |>
  mutate(
    cohort = if_else(unit <= 10, 4, 8),
    treated = as.integer(period >= cohort),
    tau = if_else(treated == 1, 0.1 * (period - cohort + 1), 0),
    outcome = 0.05 * period + tau
  )
toy_twfe <- coef(feols(outcome ~ treated | unit + period, vcov = ~unit, data = toy))[["treated"]]
toy_att <- mean(toy$tau[toy$treated == 1])
toy_mean <- function(g, periods) mean(toy$outcome[toy$cohort == g & toy$period %in% periods])
toy_early_late <- (toy_mean(4, 4:7) - toy_mean(4, 1:3)) - (toy_mean(8, 4:7) - toy_mean(8, 1:3))
toy_late_early <- (toy_mean(8, 8:10) - toy_mean(8, 4:7)) - (toy_mean(4, 8:10) - toy_mean(4, 4:7))
toy |>
  summarise(.by = c(period, cohort), outcome = mean(outcome)) |>
  mutate(cohort = paste("Adopts week", cohort)) |>
  ggplot(aes(x = period, y = outcome, color = cohort)) +
  annotate("rect", xmin = 3.5, xmax = 10.5, ymin = -Inf, ymax = Inf, alpha = 0.08) +
  geom_vline(xintercept = c(4, 8), linetype = "dashed", color = "grey40") +
  geom_line() +
  geom_point(size = 2) +
  labs(x = "Week", y = "Outcome", color = NULL, caption = "Shaded: window of the later-vs-earlier comparison") +
  week_axis +
  theme(legend.position = "bottom")
```

The toy panel has no noise, a common trend, and an effect that rises by 0.1 each week after adoption.

## The toy panel's 2×2s

- True ATT: `r fmt(toy_att)`
- Earlier vs later (weeks 1–7): `r fmt(toy_early_late)`
- Later vs earlier (weeks 4–10): `r fmt(toy_late_early)`. The early cohort's rising effect is subtracted.
- TWFE: `r fmt(toy_twfe)`, about `r round(100 * toy_twfe / toy_att)`% of the true ATT.

## Decomposing Case 05

```{r}
#| label: bacon-functions
# Goodman-Bacon decomposition from bacondecomp, with the comparison types
# relabelled to match the table on the "TWFE averages 2×2s" slide.
bacon_types <- c(
  "Treated vs Untreated" = "Treated vs never treated",
  "Earlier vs Later Treated" = "Earlier vs later",
  "Later vs Earlier Treated" = "Later vs earlier (already treated)"
)
decompose <- function(d) {
  out <- bacon(outcome ~ treated, data = d, id_var = "unit_id", time_var = "period", quietly = TRUE)
  out$type <- unname(bacon_types[as.character(out$type)])
  out
}

bacon_summary <- function(bd) {
  bd |>
    summarise(
      .by = type,
      `Number of 2×2s` = n(),
      `Total weight` = sum(weight),
      `Weighted mean 2×2` = sum(weight * estimate) / sum(weight)
    ) |>
    rename(Comparison = type)
}
```

```{r}
#| label: bacon-05
bacon_05 <- decompose(d05)
twfe_05 <- coef_se(feols(outcome ~ treated | unit_id + period, vcov = ~unit_id, data = d05))
knitr::kable(bacon_summary(bacon_05), digits = 3)
```

From `bacondecomp::bacon()`. Identity check: $\sum_j s_j \hat\beta_j =$ `r fmt(sum(bacon_05$weight * bacon_05$estimate), 4)`; TWFE $\hat\beta =$ `r fmt(twfe_05[1], 4)`.

## Every 2×2, by weight: Case 04 against Case 05

```{r}
#| label: bacon-plot
#| fig-height: 4.2
bacon_04 <- decompose(d04)
twfe_04 <- coef_se(feols(outcome ~ treated | unit_id + period, vcov = ~unit_id, data = d04))
bind_rows(
  bacon_04 |> mutate(case = "Case 04: constant effect", twfe = twfe_04[1]),
  bacon_05 |> mutate(case = "Case 05: growing effect", twfe = twfe_05[1])
) |>
  ggplot(aes(x = estimate, y = weight, color = type, shape = type)) +
  geom_vline(aes(xintercept = twfe), linetype = "dashed", color = "grey40") +
  geom_point(size = 3) +
  facet_wrap(~case) +
  labs(
    x = "2×2 DiD estimate",
    y = "Weight in TWFE",
    color = NULL,
    shape = NULL,
    caption = "Dashed line: TWFE estimate"
  ) +
  theme(legend.position = "bottom", legend.direction = "vertical")
```

In Case 05 the later-vs-earlier comparisons turn negative: they subtract the early cohorts' growing effects.

## Case 04 for contrast: same timing, constant effect

```{r}
#| label: bacon-04
knitr::kable(bacon_summary(bacon_04), digits = 3)
```

The weights match Case 05's. With a constant effect, every 2×2 recovers it.

## Case 05: choose the average {.smaller}

```{r}
#| label: cs-aggregations
cs_fit_05 <- fit_cs(d05)
cs_fit_05_nyt <- fit_cs(d05, control_group = "notyettreated")
agg_types <- c(simple = "Simple: all treated cells", group = "By cohort, then averaged", dynamic = "By event time, then averaged", calendar = "By calendar week, then averaged")
agg_rows <- lapply(names(agg_types), function(type) {
  never <- cs_agg(cs_fit_05, type)
  nyt <- cs_agg(cs_fit_05_nyt, type)
  data.frame(
    Aggregation = agg_types[[type]],
    `Never-treated controls` = never$overall.att,
    `Not-yet-treated controls` = nyt$overall.att,
    check.names = FALSE
  )
})
knitr::kable(do.call(rbind, agg_rows), digits = 3)
```

Each row answers a different question; pick the one that matches the estimand. Not-yet-treated controls add power but require no anticipation among later adopters.

# Case 06: spillovers

## Case 06: promotions spill over to nearby stores

```{r}
#| label: case06-means
#| fig-height: 4.4
d06 <- read_case("06")
g06 <- first_adoption(d06)
d06 <- d06 |>
  mutate(exposure = case_when(
    ever_treated == 1 ~ "Promoted store",
    distance_to_treated == 1 ~ "Nearby untreated",
    TRUE ~ "Distant untreated"
  ))
d06 |>
  summarise(.by = c(period, exposure), mean_outcome = mean(outcome)) |>
  mutate(.by = exposure, change = mean_outcome - mean(mean_outcome[period < g06])) |>
  ggplot(aes(x = period, y = change, color = exposure, shape = exposure)) +
  geom_vline(xintercept = g06, linetype = "dashed", color = "grey40") +
  geom_line() +
  geom_point(size = 2) +
  labs(x = "Week", y = "Change from own pre-launch mean", color = NULL, shape = NULL) +
  week_axis +
  theme(legend.position = "bottom")
```

## Case 06: controls must be unexposed

```{r}
#| label: case06-table
twfe_06 <- coef_se(feols(outcome ~ treated | unit_id + period, vcov = ~unit_id, data = d06))
far_06 <- coef_se(feols(outcome ~ treated | unit_id + period, vcov = ~unit_id, data = filter(d06, ever_treated == 1 | distance_to_treated >= 5)))
near_06 <- coef_se(feols(outcome ~ treated | unit_id + period, vcov = ~unit_id, data = filter(d06, ever_treated == 1 | distance_to_treated == 1)))
estimate_table(
  c("All untreated stores as controls", "Distant stores only", "Nearby stores only"),
  c(twfe_06[1], far_06[1], near_06[1]),
  c(twfe_06[2], far_06[2], near_06[2]),
  "06"
)
```

Nearby stores gain from the promotion too, so using them as controls removes part of the effect. Define exposure before choosing controls.

# Case 07: effects that differ across stores

## Case 07: does app ordering work better in urban stores?

```{r}
#| label: case07-means
#| fig-height: 4.2
d07 <- read_case("07")
g07 <- first_adoption(d07)
d07 <- d07 |>
  mutate(
    group = if_else(ever_treated == 1, "Treated", "Control"),
    location = if_else(urban == 1, "Urban", "Rural"),
    treated_urban = treated * urban,
    ever_treated_urban = ever_treated * urban
  )
d07 |>
  summarise(.by = c(period, location, group), mean_outcome = mean(outcome)) |>
  ggplot(aes(
    x = period,
    y = mean_outcome,
    color = location,
    linetype = group,
    shape = group,
    group = interaction(location, group)
  )) +
  geom_vline(xintercept = g07, linetype = "dashed", color = "grey40") +
  geom_line() +
  geom_point(size = 2) +
  labs(
    title = "Case 07: means by treatment and location",
    x = "Week",
    y = "Mean log revenue",
    color = "Location",
    linetype = NULL,
    shape = NULL
  ) +
  week_axis +
  theme(legend.position = "bottom")
```

```{r}
#| label: case07-counts
counts_07 <- d07 |>
  distinct(unit_id, urban, ever_treated) |>
  count(urban, ever_treated)
n07 <- function(u, e) counts_07$n[counts_07$urban == u & counts_07$ever_treated == e]
```

Urban stores adopt more often (`r n07(1, 1)` of `r n07(1, 1) + n07(1, 0)`, against `r n07(0, 1)` of `r n07(0, 1) + n07(0, 0)` rural stores) and grow faster whether or not they adopt.

## One DiD per location {.smaller}

Target: the ATT within each location $m$, and their difference.

$$
\text{ATT}(m) = \mathbb{E}\big[\,Y_{it}(1) - Y_{it}(0) \mid \text{treated},\ \text{urban}_i = m,\ t \ge g\,\big]
$$

Assumption: parallel trends **within each location** $m$, not across locations:

$$
\mathbb{E}\big[\Delta Y_{it}(0) \mid \text{treated},\ \text{urban}_i = m\big] = \mathbb{E}\big[\Delta Y_{it}(0) \mid \text{control},\ \text{urban}_i = m\big]
$$

Urban stores may trend differently from rural stores. Each location's treated stores are compared only with that location's controls.

```{r}
#| label: case07-2x2
changes_07 <- d07 |>
  mutate(post = period >= g07) |>
  summarise(.by = c(location, ever_treated), change = mean(outcome[post]) - mean(outcome[!post]))
by_hand_07 <- changes_07 |>
  summarise(
    .by = location,
    `Treated change` = change[ever_treated == 1],
    `Control change` = change[ever_treated == 0]
  ) |>
  mutate(DiD = `Treated change` - `Control change`) |>
  arrange(location) |>
  rename(Location = location)
did_rural_07 <- by_hand_07$DiD[by_hand_07$Location == "Rural"]
did_urban_07 <- by_hand_07$DiD[by_hand_07$Location == "Urban"]
knitr::kable(by_hand_07, digits = 3)
```

Urban minus rural: `r fmt(did_urban_07)` − `r fmt(did_rural_07)` = `r fmt(did_urban_07 - did_rural_07)`. This is the triple difference.

## The same numbers from one regression {.smaller}

$$
y_{it} = \alpha_i + \lambda_{t,\,\text{urban}_i} + \beta\, D_{it} + \gamma\, D_{it}\cdot\text{urban}_i + \varepsilon_{it}
$$

```{r}
#| label: case07-triple
#| echo: true
triple_fit_07 <- feols(
  outcome ~ treated + treated_urban | unit_id + period^urban,
  vcov = ~unit_id,
  data = d07
)
```

```{r}
#| label: case07-triple-result
beta_07 <- coef_se(triple_fit_07, "treated")
gamma_07 <- coef_se(triple_fit_07, "treated_urban")
```

- `period^urban` gives each location its own week effects $\lambda_{t,\text{urban}}$: parallel trends are imposed within each location only.
- $\hat\beta =$ `r fmt(beta_07[1])`: the rural DiD. $\hat\beta + \hat\gamma =$ `r fmt(beta_07[1] + gamma_07[1])`: the urban DiD.
- $\hat\gamma =$ `r fmt(gamma_07[1])` (SE `r fmt(gamma_07[2])`): the difference between locations.

## Same as one regression per location {.smaller}

```{r}
#| label: case07-split
#| echo: true
location_fit_07 <- feols(outcome ~ i(urban, treated) | unit_id + period^urban,
                         vcov = ~unit_id, data = d07)
separate_fits_07 <- feols(outcome ~ treated | unit_id + period,
                          split = ~urban, vcov = ~unit_id, data = d07)
```

```{r}
#| label: case07-split-table
data.frame(
  Location = c("Rural", "Urban"),
  `Separate: estimate` = sapply(separate_fits_07, coef),
  `SE` = sapply(separate_fits_07, se),
  `Pooled: estimate` = unname(coef(location_fit_07)),
  `SE ` = unname(se(location_fit_07)),
  check.names = FALSE,
  row.names = NULL
) |>
  knitr::kable(digits = c(0, 4, 5, 4, 5))
```

- Each store belongs to one location, and each location has its own week effects, so the pooled model shares nothing across locations. It reproduces each location's TWFE exactly, and $\hat\gamma$ is the difference of the two separate estimates.
- The standard errors differ only through fixest's small-sample correction, which counts all stores in the pooled model.

## Case 07: leave out location-by-week effects {.smaller}

```{r}
#| label: case07-table
omit_fit_07 <- feols(outcome ~ treated + treated_urban | unit_id + period, vcov = ~unit_id, data = d07)
twfe_07 <- coef_se(feols(outcome ~ treated | unit_id + period, vcov = ~unit_id, data = d07))
urban_share_07 <- mean(d07$urban[d07$ever_treated == 1 & d07$period == 1])
att_w_07 <- c(1 - urban_share_07, urban_share_07)
att_triple_07 <- sum(att_w_07 * coef(location_fit_07))
att_triple_se_07 <- sqrt(drop(t(att_w_07) %*% vcov(location_fit_07) %*% att_w_07))
omit_beta_07 <- coef_se(omit_fit_07, "treated")
omit_gamma_07 <- coef_se(omit_fit_07, "treated_urban")
table_07 <- data.frame(
  Quantity = c("Rural effect", "Urban minus rural", "ATT, all treated stores"),
  `Location-by-week effects` = c(beta_07[1], gamma_07[1], att_triple_07),
  SE = c(beta_07[2], gamma_07[2], att_triple_se_07),
  `Common week effects` = c(omit_beta_07[1], omit_gamma_07[1], twfe_07[1]),
  `SE ` = c(omit_beta_07[2], omit_gamma_07[2], twfe_07[2]),
  check.names = FALSE
)
if (show_truth) {
  truth_07 <- read_truth("07") |> filter(treated == 1)
  planted_07 <- tapply(truth_07$tau, truth_07$urban, mean)
  table_07$Planted <- c(planted_07[["0"]], planted_07[["1"]] - planted_07[["0"]], mean(truth_07$tau))
}
knitr::kable(table_07, digits = 3)
```

- With common week effects, the urban stores' own trend is counted as treatment effect: the moderation coefficient compares urban with rural **treated** stores only.
- The last row pools both locations. Treated stores are mostly urban, so the pooled two-group TWFE inherits the urban trend too.

## Case 07: check pre-trends within each location

```{r}
#| label: case07-event
#| fig-height: 3.8
event_formula_07 <- function(fe) {
  as.formula(sprintf(
    "outcome ~ i(period, ever_treated, ref = %d) + i(period, ever_treated_urban, ref = %d) | unit_id + %s",
    g07 - 1L, g07 - 1L, fe
  ))
}
event_fit_07 <- feols(event_formula_07("period^urban"), vcov = ~unit_id, data = d07)
event_omit_07 <- feols(event_formula_07("period"), vcov = ~unit_id, data = d07)
pre_p_07 <- function(fit) {
  wald(fit, keep = sprintf("^period::(%s):ever_treated_urban$", paste(seq_len(g07 - 2L), collapse = "|")), print = FALSE)$p
}
urban_leads_07 <- function(fit, label) {
  ct <- coeftable(fit)
  keep <- grepl(":ever_treated_urban$", rownames(ct))
  data.frame(
    event_time = as.integer(sub("^period::(-?[0-9]+):.*$", "\\1", rownames(ct)[keep])),
    estimate = unname(ct[keep, "Estimate"]),
    se = unname(ct[keep, "Std. Error"])
  ) |>
    bind_rows(data.frame(event_time = g07 - 1L, estimate = 0, se = 0)) |>
    mutate(specification = label)
}
bind_rows(
  urban_leads_07(event_fit_07, "Location-by-week effects"),
  urban_leads_07(event_omit_07, "Common week effects")
) |>
  ggplot(aes(x = event_time, y = estimate, color = specification)) +
  geom_hline(yintercept = 0, color = "grey50") +
  geom_vline(xintercept = g07 - 0.5, linetype = "dashed", color = "grey40") +
  geom_pointrange(
    aes(ymin = estimate - 1.96 * se, ymax = estimate + 1.96 * se),
    position = position_dodge(width = 0.5),
    size = 0.3
  ) +
  labs(x = "Week (week 6 is the reference)", y = "Urban minus rural, 95% CI", color = NULL) +
  week_axis +
  theme(legend.position = "bottom")
```

Joint test that the urban-minus-rural leads in weeks 1–5 are zero: p = `r fmt(pre_p_07(event_fit_07))` with location-by-week effects, p = `r fmt(pre_p_07(event_omit_07), 4)` with common week effects.

## Reading a moderated DiD

- $\gamma$ says the effect **differs** between urban and rural stores. It does not say that making a store urban would raise the effect: urban stores differ in many other ways.
- The moderator must be fixed before treatment and observed for control stores too. A moderator that treatment can change, or that exists only for treated stores, breaks the within-location comparison.
- Interaction terms need far more data than a main effect. A wide confidence interval on $\gamma$ is not evidence that the effect is the same everywhere.

# What pre-tests can and cannot show

## Pre-tests across the cases {.smaller}

```{r}
#| label: pretest-table
pretest_cases <- data.frame(
  case = c("01", "02", "03", "06", "08"),
  issue = c(
    "Clean benchmark", "Composition differences", "Pre-adoption dip",
    "Spillovers", "Bad control"
  )
)
pretest_rows <- lapply(seq_len(nrow(pretest_cases)), function(r) {
  id <- pretest_cases$case[r]
  d <- read_case(id)
  g <- first_adoption(d)
  out <- data.frame(
    Case = id,
    Issue = pretest_cases$issue[r],
    `Pre-test p` = pre_test_p(fit_event(d, g - 1L), g - 1L),
    `TWFE estimate` = coef(feols(outcome ~ treated | unit_id + period, vcov = ~unit_id, data = d))[["treated"]],
    check.names = FALSE
  )
  if (show_truth) out$`Planted ATT` <- true_att(id)
  out
})
knitr::kable(do.call(rbind, pretest_rows), digits = 3)
```

A rejection signals a problem, but a pass does not rule one out: spillovers (06) and bad controls (08) leave the pre-period untouched.

## Pre-tests have low power

```{r}
#| label: pretest-power
power_rows <- lapply(c(0, 0.005, 0.01, 0.015, 0.02), function(slope) {
  d <- d01 |> mutate(outcome = outcome + slope * period * ever_treated)
  data.frame(
    `Added trend per week (treated)` = slope,
    `Bias in TWFE` = coef(feols(outcome ~ treated | unit_id + period, vcov = ~unit_id, data = d))[["treated"]] - twfe_01[1],
    `Pre-test p` = pre_test_p(fit_event(d, g01 - 1L), g01 - 1L),
    check.names = FALSE
  )
})
knitr::kable(do.call(rbind, power_rows), digits = 3)
```

Each row adds a linear trend to Case 01's treated stores. A trend that passes the pre-test can still shift the estimate noticeably.

## After a pre-test

- Reporting only designs that pass a pre-test biases the published estimates (Roth 2022).
- Instead, bound how far the post-launch violation may exceed the pre-launch one and report how the estimate changes (Rambachan and Roth 2023, `HonestDiD`).

## Parallel trends depend on the outcome scale {.smaller}

Control stores go from 100 to 110. Treated stores start at 200.

| Assumption | Treated counterfactual |
|---|---|
| Parallel trends in **levels** | 210 (+5%) |
| Parallel trends in **logs** | 220 (+10%) |

Both can hold only if the groups start at the same level or nothing changes (Roth and Sant'Anna 2023).

```{r}
#| label: scale-levels
levels_01 <- d01 |>
  filter(period < g01) |>
  summarise(.by = ever_treated, level = mean(exp(outcome)))
```

In Case 01, pre-launch revenue is `r fmt(levels_01$level[levels_01$ever_treated == 1], 2)` (treated) and `r fmt(levels_01$level[levels_01$ever_treated == 0], 2)` (control), so the scale matters little there.

More on how the scale changes the estimand: [didestimands.app](https://didestimands.app).

# Optional: Case 08

## Case 08: advertising raises engagement

```{r}
#| label: case08-means
#| fig-height: 4.2
d08 <- read_case("08")
g08 <- first_adoption(d08)
d08_means <- d08 |>
  mutate(group = if_else(ever_treated == 1, "Treated", "Control")) |>
  summarise(.by = c(period, group), Outcome = mean(outcome), Engagement = mean(engagement))
d08_means <- bind_rows(
  transmute(d08_means, period, group, measure = "Outcome", value = Outcome),
  transmute(d08_means, period, group, measure = "Engagement", value = Engagement)
)
d08_means |>
  ggplot(aes(x = period, y = value, color = group, shape = group)) +
  geom_vline(xintercept = g08, linetype = "dashed", color = "grey40") +
  geom_line() +
  geom_point(size = 2) +
  facet_wrap(~measure, scales = "free_y") +
  labs(x = "Week", y = "Mean", color = NULL, shape = NULL) +
  week_axis +
  theme(legend.position = "bottom")
```

## Case 08: controlling for a mediator

```{r}
#| label: case08-table
total_08 <- coef_se(feols(outcome ~ treated | unit_id + period, vcov = ~unit_id, data = d08))
bad_08 <- coef_se(feols(outcome ~ treated + engagement | unit_id + period, vcov = ~unit_id, data = d08))
estimate_table(
  c("TWFE without engagement", "TWFE controlling for engagement"),
  c(total_08[1], bad_08[1]),
  c(total_08[2], bad_08[2]),
  "08"
)
```

Controlling for engagement removes the effect that runs through it, leaving the direct effect`r if (show_truth) paste0(' (planted ', fmt(mean(read_truth("08")$direct_effect[read_truth("08")$treated == 1]), 2), ')') else ''`. Use only covariates measured before treatment.

# Wrap-up

## What each case needed {.smaller}

::: {style="font-size: 85%"}
```{r}
#| label: summary
summary_table <- data.frame(
  Case = c("01", "02", "03", "04", "05", "06", "08", "07"),
  Issue = c(
    "Clean benchmark", "Composition differences", "Pre-adoption dip",
    "Staggered, constant effect",
    "Staggered, growing effect", "Spillovers", "Effect moderation",
    "Bad control"
  ),
  `Naive TWFE` = c(
    twfe_01[1], twfe_02[1], twfe_03[1],
    stagger_table$Estimate[stagger_table$Case == "04" & stagger_table$Estimator == "TWFE"],
    twfe_05[1], twfe_06[1], twfe_07[1], bad_08[1]
  ),
  Response = c(
    "TWFE", "Callaway–Sant'Anna IPW", "Callaway–Sant'Anna, anticipation = 2",
    "Callaway–Sant'Anna",
    "Callaway–Sant'Anna", "Distant controls",
    "Triple difference, location-by-week effects", "Drop the mediator"
  ),
  `Response estimate` = c(
    twfe_01[1], cs_02$overall.att, cs_dip_03$overall.att,
    stagger_table$Estimate[stagger_table$Case == "04" & stagger_table$Estimator == "Callaway–Sant'Anna"],
    stagger_table$Estimate[stagger_table$Case == "05" & stagger_table$Estimator == "Callaway–Sant'Anna"],
    far_06[1], att_triple_07, total_08[1]
  ),
  check.names = FALSE
)
if (show_truth) {
  summary_table$`Planted ATT` <- vapply(summary_table$Case, true_att, numeric(1))
}
knitr::kable(summary_table, digits = 3, row.names = FALSE)
```
:::

## Checklist before reporting a DiD

1. Plot treatment timing and group means.
2. State the estimand: which units, weeks, and average.
3. Defend the comparison group: parallel trends, no anticipation, no spillovers.
4. Adjust only for pre-treatment covariates; check overlap.
5. With staggered timing, use Callaway–Sant'Anna or Sun–Abraham.
6. Treat pre-tests as diagnostics; add a sensitivity analysis.
7. Cluster at the level of treatment assignment.

## References {.smaller}

- Arkhangelsky, D., Athey, S., Hirshberg, D. A., Imbens, G. W., & Wager, S. (2021). Synthetic difference-in-differences. *American Economic Review*, 111(12), 4088–4118.
- Callaway, B., & Sant'Anna, P. H. C. (2021). Difference-in-differences with multiple time periods. *Journal of Econometrics*, 225(2), 200–230.
- de Chaisemartin, C., & D'Haultfœuille, X. (2020). Two-way fixed effects estimators with heterogeneous treatment effects. *American Economic Review*, 110(9), 2964–2996.
- Goodman-Bacon, A. (2021). Difference-in-differences with variation in treatment timing. *Journal of Econometrics*, 225(2), 254–277.

## References (continued) {.smaller}

- Rambachan, A., & Roth, J. (2023). A more credible approach to parallel trends. *Review of Economic Studies*, 90(5), 2555–2591.
- Roth, J. (2022). Pretest with caution: Event-study estimates after testing for parallel trends. *American Economic Review: Insights*, 4(3), 305–322.
- Roth, J., & Sant'Anna, P. H. C. (2023). When is parallel trends sensitive to functional form? *Econometrica*, 91(2), 737–747.
- Sun, L., & Abraham, S. (2021). Estimating dynamic treatment effects in event studies with heterogeneous treatment effects. *Journal of Econometrics*, 225(2), 175–199.
